---
title: "Sample Forecast Dashboard"
author: "Stuart Jennings"
resource_files:
- update_files.R
output:
  flexdashboard::flex_dashboard:
    logo: data/test2.png
    theme: flatly
    social: menu
    source_code: embed
runtime: shiny
---
<style>                     
.navbar {
  background-color:lavender;
  border-color:black;
}
.navbar-brand {
color:black!important;
}
.navmenu {
color:black!important;
}
</style>

<script>
$('.navbar-logo').wrap('<a href="http://www.doterra.com" target=_blank>');
</script>

```{r, echo=FALSE}
# add fun team logo at bottom left
 htmltools::img(src = knitr::image_uri(file.path("data/cit_full.png")),
                alt = 'CIT logo', 
                style = 'position:fixed; bottom:10px; left:10px; padding:10px;')

# add loading gif in middle of screen (some scaling issues on large monitors)
 htmltools::img(src = knitr::image_uri(file.path("data/timer.gif.gif")),
                alt = 'Loading...',
                style = 'position:absolute; width:100px; height:100px; right:550px; bottom:300px; padding:10px;')
```

```{r global, include=FALSE}
# load packages
library(tidyverse)
library(lubridate)
library(flexdashboard)
library(plotly)
library(shiny)
library(openxlsx)
library(data.table)

# initialize number of days passed in the month
days_passed <- 21

##--------------------------------------MARKET 1 DATA-------------------------------------

# Read in data files
mkt1_data <- read.csv("data/market1_data.csv", skip = 3, header = TRUE)
old_mkt1 <- read.csv("data/market1_old.csv", skip = 2)

mkt1_forecast <- read.xlsx("data/market1 Forecast.xlsx", sheet = length(getSheetNames("data/market1 Forecast.xlsx")), detectDates = TRUE)

names(mkt1_forecast) <- c("Day", "Lower 80%", "Forecast", "Upper 80%")

##-------------------------------------MARKET 2 DATA---------------------------------------

# Read in data files
mkt2_data <- read.csv("data/market2_data.csv", skip = 3, header = TRUE)
old_mkt2 <- read.csv("data/market2_old.csv", skip = 3)
mkt2_forecast<- read.xlsx("data/market2 Forecast.xlsx", sheet = length(getSheetNames("data/market2 Forecast.xlsx")), detectDates = TRUE)

names(mkt2_forecast) <- c("Day", "Lower 80%", "Forecast", "Upper 80%")

##-------------------------------------MARKET 3 DATA---------------------------------------

# Read in data files
mkt3_data <- read.csv("data/market3_data.csv", skip = 3, header = TRUE)
old_mkt3 <- read.csv("data/market3_old.csv", skip = 4)
mkt3_forecast<- read.xlsx("data/market3 Forecast.xlsx", sheet = length(getSheetNames("data/market3 Forecast.xlsx")), detectDates = TRUE)

names(mkt3_forecast) <- c("Day", "Lower 80%", "Forecast", "Upper 80%")

##--------------------------------------MARKET 4 DATA--------------------------------------

# Read in data files
mkt4_data <- read.csv("data/market4_data.csv", skip = 3, header = TRUE)
old_mkt4 <- read.csv("data/market4_old.csv", skip = 3)
mkt4_forecast <- read.xlsx("data/market4 Forecast.xlsx", sheet = length(getSheetNames("data/market4 Forecast.xlsx")), detectDates = TRUE)

names(mkt4_forecast) <- c("Day", "Lower 80%", "Forecast", "Upper 80%")
```

Sidebar {.sidebar}
=====================================

This is a sample interactive dashboard of call forecasts for different markets.

First, select your market at the top of the page, and view your desired forecast by following the instructions below.

**Step 1**

```{r}
# protect data with password
passwordInput("pwIn", label = "Enter password (pass123):")
```

**Step 2**

```{r}
# date range selector
dateRangeInput("inDateRange", "Select the number of days you wish to predict:",
               end = "2020-12-31")
```

**Step 3**

Feel free to explore the zooming and window options found on the top left!

**Step 4** 

Profit!

```{r}
# Build graphing function to use for each market

graph <- function(date1 = "2018-05-20", date2 = paste0("2020-01-", days_passed), fc_len = "2020-12-31", ts, fc, skill, type = "Arrivals", ci95 = FALSE){

  datad <- seq(as.Date(date1), as.Date(date2), by = 1) 
  
  predd <- reactive({
    seq(as.Date(input$inDateRange[1], origin = "1970-01-01"), as.Date(input$inDateRange[2], origin = "1970-01-01"), by = 1)
    })
  
  # Plot data along with forecast
  renderPlotly({
    # add password protection (not super secure...) and validate field selection
    validate(
      need(input$pwIn=="pass123", "Please enter the password to view the data!"),
      need(input$inDateRange[2] <= as.Date(fc_len), paste0("ERROR: Please enter a valid date (forecast extends to ", fc_len, ")!")),
      need(input$inDateRange[1] == today(tzone = "MST"), "ERROR: Start date must be the current date!"),
      need(input$inDateRange[2] >= today(tzone = "MST"), "ERROR: End date must be greater than or equal to the current date!")
    )
    # build graph for forecasts with only 80% CIs
    if (ci95 == FALSE) {
      plot_ly() %>%
        # add historical data
        add_lines(x = datad, y = ts,
                  color = I("black"), name = "observed") %>%
        # add 80% CI
        add_ribbons(x = predd(),
                    ymin = fc$`Lower 80%`[fc$Day %between% c(input$inDateRange[1], input$inDateRange[2])],
                    ymax = fc$`Upper 80%`[fc$Day %between% c(input$inDateRange[1], input$inDateRange[2])],
                    color = I("royalblue1"),
                    name = "80% confidence") %>%
        # add forecast
        add_lines(x = predd(),
                  y = fc$Forecast[fc$Day %between% c(input$inDateRange[1], input$inDateRange[2])],
                  color = I("blue"),
                  name = "prediction") %>% 
        layout(title = paste(skill, type, "Forecast", sep = " "),
               xaxis = list(title = "Date"),
               yaxis = list(title = paste("Daily", type, sep = " "),
                            rangemode = "nonnegative"))
    }
    else { # build graph for 95% CI forecasts
      plot_ly() %>%
        # add historical data
        add_lines(x = datad, y = ts,
                  color = I("black"), name = "observed") %>%
        # add 95% CI
        add_ribbons(x = predd(),
                    ymin = fc$`Lower 95%`[fc$Day %between% c(input$inDateRange[1],input$inDateRange[2])],
                    ymax = fc$`Upper 95%`[fc$Day %between% c(input$inDateRange[1], input$inDateRange[2])],
                    color = I("lightskyblue"),
                    name = "95% confidence") %>%
        # add 80% CI
        add_ribbons(x = predd(),
                    ymin = fc$`Lower 80%`[fc$Day %between% c(input$inDateRange[1], input$inDateRange[2])],
                    ymax = fc$`Upper 80%`[fc$Day %between% c(input$inDateRange[1], input$inDateRange[2])],
                    color = I("royalblue1"),
                    name = "80% confidence") %>%
        # add forecast
        add_lines(x = predd(),
                  y = fc$Forecast[fc$Day %between% c(input$inDateRange[1], input$inDateRange[2])],
                  color = I("blue"),
                  name = "prediction") %>% 
        layout(title = paste(skill, type, "Forecast", sep = " "),
               xaxis = list(title = "Date"),
               yaxis = list(title = paste("Daily", type, sep = " "),
                            rangemode = "nonnegative")) 
    }
  })
}
```

Market 1 {data-navmenu="Calls" data-icon="fa-football-ball"}
===================================== 

### Arrivals Forecast

```{r}
# Select only date and call columns
mkt1_calls <- mkt1_data[-1,c(1,5)]
old_mkt1 <- old_mkt1[-374, c(1,4)]
names(old_mkt1) <- c("Date", "Arrivals")

# Join data files to account for disappearing May '18 data
mkt1_calls <- dplyr::union(old_mkt1, mkt1_calls)

ts1 <- ts(mkt1_calls$Arrivals, frequency = 7)

graph(ts = ts1, fc = mkt1_forecast, skill = "Market 1")
```

Market 2 {data-navmenu="Calls" data-icon="fa-futbol"}
===================================== 

### Arrivals Forecast

```{r}
##----------------------------------MARKET 2 NOW-----------------------------------------

# Select only date and call columns
mkt2_calls <- mkt2_data[-1,c(1,5)]
old_mkt2 <- old_mkt2[, c(1,4)]
names(old_mkt2) <- c("Date", "Arrivals")

# Join data files to account for disappearing May '18 data
mkt2_calls <- dplyr::union(old_mkt2, mkt2_calls)

ts2 <- ts(mkt2_calls$Arrivals, frequency = 7)

graph(ts = ts2, fc = mkt2_forecast, skill = "Market 2")
```

Market 3 {data-navmenu="Calls" data-icon="fa-money-check-alt"}
===================================== 

### Arrivals Forecast

```{r}
##----------------------------------MARKET 3 NOW-----------------------------------------

# Select only date and call columns
mkt3_calls <- mkt3_data[-1,c(1,5)]
old_mkt3 <- old_mkt3[, c(1,5)]
names(old_mkt3) <- c("Date", "Arrivals")

# Join data files to account for disappearing May '18 data
mkt3_calls <- dplyr::union(old_mkt3, mkt3_calls)

ts3 <- ts(mkt3_calls$Arrivals, frequency = 7)

graph(ts = ts3, fc = mkt3_forecast, skill = "Market 3")
```

Market 4 {data-navmenu="Calls" data-icon="fa-hockey-puck"}
===================================== 

### Arrivals Forecast

```{r}
##----------------------------------------MARKET 4 NOW---------------------------------------------

# Select only date and call columns
mkt4_calls <- mkt4_data[-1,c(1,5)]
old_mkt4 <- old_mkt4[-1, c(1,5)]
names(old_mkt4) <- c("Date", "Arrivals")

# Join data files to account for disappearing May '18 data
mkt4_calls <- dplyr::union(old_mkt4, mkt4_calls)

ts35 <- ts(mkt4_calls$Arrivals, frequency = 7)

graph(date1 = "2018-05-23", ts = ts35, fc = mkt4_forecast, skill = "Market 4")
```
